\textbf{Honeypot Assignment: \\ \emph{Group Contagiarium}}

### 2012-01-05 Paper_honeypot.tex
Intro toegevoegd

\newcommand{\tocheck}[1]{{\bf !?: #1 :!?}}
\newcommand{\OBA}{Online behavioural advertising }
\newcommand{\oba}{online behavioural advertising }
\newcommand{\ePD}{ePrivacy Directive }
\newcommand{\DPD}{Data Protection Directive }

@@

\title{\textbf{Law in Cyberspace\\ \emph{Web Analytics and Online Personalisation}}}
\author{Aram Verstegen, \tocheck{studentnummer Utwente} \\
	 Mark Vijfvinkel, 1275194 \\
	 Bart Lutgens, \tocheck{studentnummer Utwente} \\
	Joost Kremers, \tocheck{studentnummer Utwente}}

@@

\section{Introduction}

@@

\section{Attacks on the different services}
\label{Attacks}

\section{Connection between the attacks}
\label{Connection}

\section{Conclusion}
\label{Conclusion}

>>>>

\newcommand{\tocheck}[1]{{\bf !?: #1 :!?}}
%\newcommand{\OBA}{Online behavioural advertising }

@@

\title{\textbf{Honeypot Assignment: \\ \emph{Group Contagiarium}}}
\author{Aram Verstegen, \tocheck{studentnummer Utwente} \\
	 Mark Vijfvinkel, 1275194 \\
	 Bart Lutgens, \tocheck{studentnummer Utwente} \\
	Joost Kremers, \tocheck{studentnummer Utwente}}

@@

\section{Introduction}
In this paper we will try to present an overview of the data we have collected from the honeypot and explain the different attacks that were waged against it. 
In the second section we will describe the changes we have made to the setup during the "Waiting for hackers" phase. 
The third section will present an overview of various statistics we have collected from the logfiles, e.g. number of IP-addresses, countries and attack types. 
In the fourth section we will discuss which attacks took place against the different services the honeypot was running e.g. SSH and MySQL.
In order to discover the sophisticationof the attacks, we will try to present possible connections between an attack on one service and an attack on a different service, in the fifth section.
The sixth section will conclude our findings. 
Finally we will discuss this project and provide some improvements.

@@

\section{Attacks on the different services}
\label{Attacks}
During phase 2 we have monitored the honeypot closely and collected data about different attacks against the honeypot. In this section we will discuss the attacks against the services the honeypot was running.

\section{Connection between the attacks}
\label{Connection}
In this section we will correlate the data about attacks against one service against the data of attacks of a different service. We will try to look for a pattern or similarities in this data and determine if the attack was more sophisticated.

\section{Conclusion}
\label{Conclusion}
From Section \ref{Connection} we can conclude that...

\section{Discussion}
\label{Discussion}
In this section we would like to discuss some issues we encountered during the honeypotproject.

\begin{itemize}
\item Low/High interaction phase
\item GHH
\item etc
\end{itemize}
